\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/sections/semi_programatically_sources_table.tex
polishing tables

\begin{table}[h]
\begin{tabularx}{\textwidth}{p{4 cm}p{6 cm}p{.5cm}X}
    \toprule
    source & description & question count \\
\midrule
Number of isomers & MAYGEN was used to compute the number of isomers for a set of SMILES extracted from the ZINC dataset. & & \variable{output/question_count_per_dir/json_file_counts_number_of_isomers.txt} \\
Total electron count of molecules & Electron counts based on the data from https://www.cheminfo.org/. & &\variable{output/question_count_per_dir/json_file_counts_electron_counts.txt} \\
Oxidation states & Oxidation states questions based on the data from https://www.cheminfo.org/. && \variable{output/question_count_per_dir/json_file_counts_oxidation_states.txt} \\
Chemical reactivity & Questions are framed based on the information from Cameo Chemicals website (https://cameochemicals.noaa.gov/reactivity). && \variable{output/question_count_per_dir/json_file_counts_reactive_groups.txt} \\
Number of NMR signals & Molecules are sampled from the ZINC database and the number of NMR signals is computed with OpenChemLib && \variable{output/question_count_per_dir/json_file_counts_number_of_nmr_peaks.txt} \\
Point group of molecules & Our ChemCaption tool is used to assign the point group, and then each case was manually checked to select well-defined cases. && \variable{output/question_count_per_dir/json_file_counts_point_group.txt} \\
IUPAC-SMILES pairs & Sampled from the PubChem database && \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} + \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} \\
\multirow{3}{*}{PubChem safety data} & Daily allowable intakes according to the World Health Organization && \variable{output/question_count_per_dir/json_file_counts_dai.txt}  \\
 & Definitions of hazard statements &&  \variable{output/question_count_per_dir/json_file_counts_h_statements.txt} \\
 & GHS classification of chemicals mined through the API& & \variable{output/question_count_per_dir/json_file_counts_pictograms.txt} \\
\multirow{2}{*}{Safety}
& Materials' compatibility && \variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} \\
 & Chemical compatibility && \variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} \\
\bottomrule
\end{tabularx}
\end{table}

>>>>

\begin{table}[h]
\begin{tabularx}{\textwidth}{p{3.5 cm}p{6.5 cm}p{.5cm}X}
    \toprule
    source & description & question count \\
\midrule
Number of isomers & MAYGEN was used to compute the number of isomers for a set of SMILES extracted from the ZINC dataset. & & \variable{output/question_count_per_dir/json_file_counts_number_of_isomers.txt} \\
\midrule
Total electron count of molecules & Electron counts based on the data from https://www.cheminfo.org/. & &\variable{output/question_count_per_dir/json_file_counts_electron_counts.txt} \\
\midrule
Oxidation states & Oxidation states questions based on the data from https://www.cheminfo.org/. && \variable{output/question_count_per_dir/json_file_counts_oxidation_states.txt} \\
\midrule
Chemical reactivity & Questions are framed based on the information from Cameo Chemicals website (https://cameochemicals.noaa.gov/reactivity). && \variable{output/question_count_per_dir/json_file_counts_reactive_groups.txt} \\
\midrule
Number of NMR signals & Molecules are sampled from the ZINC database and the number of NMR signals is computed with OpenChemLib && \variable{output/question_count_per_dir/json_file_counts_number_of_nmr_peaks.txt} \\
\midrule
Point group of molecules & Our ChemCaption tool is used to assign the point group, and then each case was manually checked to select well-defined cases. && \variable{output/question_count_per_dir/json_file_counts_point_group.txt} \\
\midrule
IUPAC-SMILES pairs & Sampled from the PubChem database && \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} + \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} \\
\midrule
\multirow{3}{*}{PubChem safety data} & Daily allowable intakes according to the World Health Organization && \variable{output/question_count_per_dir/json_file_counts_dai.txt}  \\
 & Definitions of hazard statements &&  \variable{output/question_count_per_dir/json_file_counts_h_statements.txt} \\
 & GHS classification of chemicals mined through the API& & \variable{output/question_count_per_dir/json_file_counts_pictograms.txt} \\
 \midrule
\multirow{2}{*}{Safety}
& Materials' compatibility && \variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} \\
 & Chemical compatibility && \variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} \\
\bottomrule
\end{tabularx}
\end{table}

### 2024-03-28 src/tex/showyourwork-metadata.tex
polishing tables

        \OnGithubActionsfalse
        \def\syw@url{https://github.com/lamalab-org/chembench-paper}
    \def\syw@slug{lamalab-org/chembench-paper}
    \def\syw@sha{e9da465b586df3b66d049cbdbf915503a23b2cb2}
    \def\syw@runid{}

@@

        \addvalue{fig:topic_barplot_script}{src/scripts/plot_statistics.py}
        \addvalue{fig:question_diversity_script}{src/scripts/plot_question_diversity.py}
        \addvalue{fig:human_vs_models_bar_script}{src/scripts/plot_overview_performance_plot.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_human_script}{src/scripts/analyze_model_reports.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_human_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:confidence_vs_performance_script}{src/scripts/joint_analysis_confidence_performance.py}
        \addvalue{fig:flesch_kincaid_reading_ease_script}{src/scripts/wordcloud.py}
        \addvalue{fig:question_count_barplot_mcq_vs_general_script}{src/scripts/plot_statistics.py}
        \addvalue{fig:barplot_all_correct_all_questions_script}{src/scripts/plot_overview_performance_plot.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_overall_script}{src/scripts/analyze_model_reports.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_overall_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:parallel_coordinates_overall_script}{src/scripts/make_parallel_coordinates_plot.py}
        \addvalue{fig:parallel_coordinates_tiny_script}{src/scripts/make_parallel_coordinates_plot.py}
        \addvalue{fig:performance_per_topic_script}{src/scripts/analyze_performance_per_source.py}
        \addvalue{fig:performance_per_topic_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:performance_per_topic_tiny_script}{src/scripts/analyze_performance_per_source.py}
        \addvalue{fig:performance_per_topic_tiny_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:reading_ease_vs_model_performance_script}{src/scripts/reading_ease_vs_model_performance.py}
        \addvalue{fig:reading_ease_vs_model_performance_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:correlation_plot_is_number_nmr_peaks_num_atoms_script}{src/scripts/correlate_with_molecule_features.py}
        \addvalue{fig:human_score_distribution_script}{src/scripts/plot_human_score_distribution.py}
        \addvalue{fig:human_timing_script}{src/scripts/analyze_human_data.py}
        \addvalue{fig:experience_vs_correctness_script}{src/scripts/analyze_human_data.py}
        \addvalue{fig:confidence_score_distributions_script}{src/scripts/plot_confidence_score_distributions.py}

@@

        \addvalue{output/question_count_per_dir/json_file_counts_ac_faessler_tum.txt_rule}{Snakefile\#L235}
        \addvalue{output/question_count_per_dir/json_file_counts_pum_tum.txt_rule}{Snakefile\#L235}

@@

        \addvalue{output/question_count_per_dir/json_file_counts_safety.txt_rule}{Snakefile\#L235}

>>>>

        \OnGithubActionsfalse
        \def\syw@url{https://github.com/lamalab-org/chembench-paper}
    \def\syw@slug{lamalab-org/chembench-paper}
    \def\syw@sha{829e14e5ec3be9b46f822ed113d6c6d6fa5fb029}
    \def\syw@runid{}

@@

        \addvalue{fig:topic_barplot_script}{src/scripts/plot_statistics.py}
        \addvalue{fig:question_diversity_script}{src/scripts/plot_question_diversity.py}
        \addvalue{fig:human_vs_models_bar_script}{src/scripts/plot_overview_performance_plot.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_human_script}{src/scripts/analyze_model_reports.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_human_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:confidence_vs_performance_script}{src/scripts/joint_analysis_confidence_performance.py}
        \addvalue{fig:flesch_kincaid_reading_ease_script}{src/scripts/wordcloud.py}
        \addvalue{fig:question_count_barplot_mcq_vs_general_script}{src/scripts/plot_statistics.py}
        \addvalue{fig:barplot_all_correct_all_questions_script}{src/scripts/plot_overview_performance_plot.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_overall_script}{src/scripts/analyze_model_reports.py}
        \addvalue{fig:all_questions_models_completely_correct_radar_overall_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:parallel_coordinates_overall_script}{src/scripts/make_parallel_coordinates_plot.py}
        \addvalue{fig:parallel_coordinates_tiny_script}{src/scripts/make_parallel_coordinates_plot.py}
        \addvalue{fig:performance_per_topic_script}{src/scripts/analyze_performance_per_source.py}
        \addvalue{fig:performance_per_topic_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:performance_per_topic_tiny_script}{src/scripts/analyze_performance_per_source.py}
        \addvalue{fig:performance_per_topic_tiny_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:reading_ease_vs_model_performance_script}{src/scripts/reading_ease_vs_model_performance.py}
        \addvalue{fig:reading_ease_vs_model_performance_cache}{https://sandbox.zenodo.org/record/34705}
        \addvalue{fig:correlation_plot_is_number_nmr_peaks_complexity_script}{src/scripts/correlate_with_molecule_features.py}
        \addvalue{fig:correlation_plot_is_number_nmr_peaks_num_atoms_script}{src/scripts/correlate_with_molecule_features.py}
        \addvalue{fig:correlation_plot_is_electron_counts_num_atoms_script}{src/scripts/correlate_with_molecule_features.py}
        \addvalue{fig:human_score_distribution_script}{src/scripts/plot_human_score_distribution.py}
        \addvalue{fig:human_timing_script}{src/scripts/analyze_human_data.py}
        \addvalue{fig:experience_vs_correctness_script}{src/scripts/analyze_human_data.py}
        \addvalue{fig:confidence_score_distributions_script}{src/scripts/plot_confidence_score_distributions.py}

@@

@@
